Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression

### 2019-04-22 Manuscript.tex
Deploy MGallow/oral_manuscript to github.com/MGallow/oral_manuscript.git:gh-pages

\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{fancyhdr} % Required for custom headers
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx}
\makeatletter
\def\thm@space@setup{%
  \thm@preskip=8pt plus 2pt minus 4pt
  \thm@postskip=\thm@preskip
}
\makeatother
\pagestyle{fancy}
% \pagestyle{empty}
\usepackage[left]{lineno} % line number package
\linenumbers % line number command
\usepackage[]{natbib}
\bibliographystyle{apalike}

\title{Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression}
\author{Matt Galloway}
\date{2019-04-21}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{1}
\tableofcontents
}
\hypertarget{intro}{%
\chapter{Introduction}\label{intro}}

@@

\begin{longtable}[]{@{}ccc@{}}
\caption{ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)
\vspace{0.5cm}}\tabularnewline
\toprule
\begin{minipage}[b]{0.14\columnwidth}\centering
model\strut
\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
error\strut
\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
sd\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.14\columnwidth}\centering
model\strut
\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
error\strut
\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
sd\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.14\columnwidth}\centering
oracleB\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
0.5056\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
0.5122\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
shrinkBO\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
2.341\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
1.014\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
shrinkB\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
2.419\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
1.083\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
ridge\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
2.479\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
1.128\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
lasso\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
2.627\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
1.27\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
shrinkBS\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
5.932\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
4.001\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
glasso\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
7.57\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
5.412\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
oracleO\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
13.18\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
10.11\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
OLS\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
14.41\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
11.24\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
oracleS\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
52.07\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
44.62\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# assume sparsity in beta}
\NormalTok{lam_max =}\StringTok{ }\KeywordTok{max}\NormalTok{(}\KeywordTok{abs}\NormalTok{(}\KeywordTok{crossprod}\NormalTok{(data}\OperatorTok{$}\NormalTok{X, data}\OperatorTok{$}\NormalTok{Y)))}
\NormalTok{(}\DataTypeTok{shrink =} \KeywordTok{shrink}\NormalTok{(}\DataTypeTok{X =}\NormalTok{ data}\OperatorTok{$}\NormalTok{X, }\DataTypeTok{Y =}\NormalTok{ data}\OperatorTok{$}\NormalTok{Y, }\DataTypeTok{B =} \KeywordTok{cov}\NormalTok{(data}\OperatorTok{$}\NormalTok{X, data}\OperatorTok{$}\NormalTok{Y), }\DataTypeTok{lam.max =}\NormalTok{ lam_max, }
    \DataTypeTok{nlam =} \DecValTok{20}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# assume sparsity in beta AND omega}
\NormalTok{(}\DataTypeTok{shrink =} \KeywordTok{shrink}\NormalTok{(}\DataTypeTok{X =}\NormalTok{ data}\OperatorTok{$}\NormalTok{X, }\DataTypeTok{Y =}\NormalTok{ data}\OperatorTok{$}\NormalTok{Y, }\DataTypeTok{B =} \KeywordTok{cbind}\NormalTok{(}\KeywordTok{cov}\NormalTok{(data}\OperatorTok{$}\NormalTok{X, data}\OperatorTok{$}\NormalTok{Y), }\KeywordTok{diag}\NormalTok{(}\KeywordTok{ncol}\NormalTok{(data}\OperatorTok{$}\NormalTok{X))), }
    \DataTypeTok{lam.max =} \DecValTok{10}\NormalTok{, }\DataTypeTok{lam.min.ratio =} \FloatTok{1e-04}\NormalTok{, }\DataTypeTok{nlam =} \DecValTok{20}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

>>>>

\usepackage{booktabs}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{fancyhdr} % Required for custom headers
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required for knitr::include_graphics
\makeatletter
\def\thm@space@setup{%
  \thm@preskip=8pt plus 2pt minus 4pt
  \thm@postskip=\thm@preskip
}
\makeatother
\pagestyle{fancy}
% \pagestyle{empty}
% \usepackage[left]{lineno} % line number package
% \linenumbers % line number command
\usepackage[]{natbib}
\bibliographystyle{apalike}

\title{Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression}
\author{Matt Galloway}
\date{2019-04-22}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{1}
\tableofcontents
}
\hypertarget{preface}{%
\chapter*{Preface}\label{preface}}

I would like to thank my advisor Professor Adam Rothman for his guidance and support this past year. His enthusiasm towards this research area is ultimately what got me interested and I truly enjoyed having the opportunity to learn from him.

My parents also deserve a note of appreciation and thanks -- one probably much longer than this. Graduate school's challenges extend far beyond the classroom and I'm so lucky to have you by my side.

\hypertarget{intro}{%
\chapter{Introduction}\label{intro}}

@@

\begin{longtable}[]{@{}ccc@{}}
\caption{Average model error for dimension p = 150.
\vspace{0.5cm}}\tabularnewline
\toprule
\begin{minipage}[b]{0.14\columnwidth}\centering
Model\strut
\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
Error\strut
\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
SD\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.14\columnwidth}\centering
Model\strut
\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
Error\strut
\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
SD\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.14\columnwidth}\centering
oracleB\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
0.5056\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
0.5122\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
shrinkBO\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
2.341\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
1.014\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
shrinkB\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
2.419\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
1.083\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
ridge\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
2.479\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
1.128\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
lasso\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
2.627\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
1.27\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
shrinkBS\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
5.932\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
4.001\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
glasso\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
7.57\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
5.412\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
oracleO\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
13.18\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
10.11\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
OLS\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
14.41\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
11.24\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering
oracleS\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
52.07\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
44.62\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# assume sparsity in beta}
\NormalTok{lam_max =}\StringTok{ }\KeywordTok{max}\NormalTok{(}\KeywordTok{abs}\NormalTok{(}\KeywordTok{crossprod}\NormalTok{(data}\OperatorTok{$}\NormalTok{X, data}\OperatorTok{$}\NormalTok{Y)))}
\NormalTok{(}\DataTypeTok{shrink =} \KeywordTok{shrink}\NormalTok{(}\DataTypeTok{X =}\NormalTok{ data}\OperatorTok{$}\NormalTok{X, }\DataTypeTok{Y =}\NormalTok{ data}\OperatorTok{$}\NormalTok{Y, }\DataTypeTok{B =} \KeywordTok{cov}\NormalTok{(data}\OperatorTok{$}\NormalTok{X, data}\OperatorTok{$}\NormalTok{Y), }
    \DataTypeTok{lam.max =}\NormalTok{ lam_max, }\DataTypeTok{nlam =} \DecValTok{20}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# assume sparsity in beta AND omega}
\NormalTok{(}\DataTypeTok{shrink =} \KeywordTok{shrink}\NormalTok{(}\DataTypeTok{X =}\NormalTok{ data}\OperatorTok{$}\NormalTok{X, }\DataTypeTok{Y =}\NormalTok{ data}\OperatorTok{$}\NormalTok{Y, }\DataTypeTok{B =} \KeywordTok{cbind}\NormalTok{(}\KeywordTok{cov}\NormalTok{(data}\OperatorTok{$}\NormalTok{X, }
\NormalTok{    data}\OperatorTok{$}\NormalTok{Y), }\KeywordTok{diag}\NormalTok{(}\KeywordTok{ncol}\NormalTok{(data}\OperatorTok{$}\NormalTok{X))), }\DataTypeTok{lam.max =} \DecValTok{10}\NormalTok{, }\DataTypeTok{lam.min.ratio =} \FloatTok{1e-04}\NormalTok{, }
    \DataTypeTok{nlam =} \DecValTok{20}\NormalTok{))}
\end{Highlighting}
\end{Shaded}
